---
title: "Abstract"
---

```{r}
library(CaviaR)
library(dplyr)

create_Timestamp<-function(start_date,no_years){
  ## create timestamp for comparison with observations
  start <- as.POSIXct(start_date)
  interval <- 60
  end <- start + as.difftime(365*no_years, units="days")
  datetime<-seq(from=start, by=interval*60*24, to=end)

  return(datetime)
   }

#Function to adjust the format of the model outputted cells to fit Excel Count tables in the standard of CaviaR.
adjustFormat<-function(cells_modelled,Year,Site){

  cells_modelled<-cells_modelled[which(cells_modelled$Year==Year),]

  summary_cz_days<-cells_modelled[which(cells_modelled$cell_type==1),]
  collect_cz<-(unique(summary_cz_days$day))
  collect<-collect_cz # a second version of cz isneeded for more clean cell collection

  summary_cz<- cells_modelled %>%
    group_by(Year,day,cell_type) %>%
    summarize(count = n()) %>%
    filter(cell_type =="1") %>%
    .$count

  collect<-data.frame(rbind(collect,summary_cz))

  #########Enlarging cells

  # If enlarging cells are not present, the dimension of the data.frame is 0 5
  # if this is the case, then there are no enlarging cells to collect,
  # only execute the below if enlarging cells are present:
  if( dim(cells_modelled[which(cells_modelled$cell_type==2),])[1]!=0){

  summary_ez_days<-cells_modelled[which(cells_modelled$cell_type==2),]
  collect_ez<-unique(summary_ez_days$day)

  summary_ez<-cells_modelled %>%
    group_by(Year,day,cell_type) %>%
    summarize(count = n()) %>%
    filter(cell_type =="2") %>%
    .$count

  collect_ez<-data.frame(rbind(collect_ez,summary_ez))

  collect <- merge(t(collect),t(collect_ez),
                         ,by.x=c('collect'),by.y=('collect_ez'),all=TRUE)
  }else{ # No enlarging cells present
    collect_ez<-collect_cz
    summary_ez<-rep(0,length(collect_cz))
    collect_ez<-data.frame(rbind(collect_ez,summary_ez))

    collect<-merge(collect,t(collect_ez),
                   by.x=c('collect'),by.y=('collect_ez'),all=TRUE)
    warning('no wall enlarging cells seem to be present in the model output, adjust format will output EZ=0 on every sample day')

  }
  #########

  # only execute the below if thickening cells are present:
  if( dim(cells_modelled[which(cells_modelled$cell_type==3),])[1]!=0){
  summary_wz_days<-cells_modelled[which(cells_modelled$cell_type==3),]
  collect_wz<-(unique(summary_wz_days$day))

  summary_wz<- cells_modelled %>%
    group_by(Year,day,cell_type) %>%
    summarize(count = n()) %>%
    filter(cell_type =="3") %>%
    .$count

  collect_wz<-data.frame(rbind(collect_wz,summary_wz))


  collect<-merge(collect,t(collect_wz),
                          ,by.x=c('collect'),by.y=('collect_wz'),all=TRUE)

  } else{ # No thickening cells present
    collect_wz<-collect_cz
    summary_wz<-rep(0,length(collect_cz))
    collect_wz<-data.frame(rbind(collect_wz,summary_wz))

    collect<-merge(collect,t(collect_wz),
                   by.x=c('collect'),by.y=('collect_wz'),all=TRUE)
    warning('no wall thickening cells seem to be present in the model output, adjust format will output WZ=0 on every sample day')

  }
  #########

  # only execute the below if mature cells are present:
  if( dim(cells_modelled[which(cells_modelled$cell_type==4),])[1]!=0){

  summary_mz_days<-cells_modelled[which(cells_modelled$cell_type==4),]
  collect_mz<-(unique(summary_mz_days$day))

  summary_mz<- cells_modelled %>%
    group_by(Year,day,cell_type) %>%
    summarize(count = n()) %>%
    filter(cell_type =="4") %>%
    .$count

  collect_mz<-data.frame(rbind(collect_mz,summary_mz))


  collect<-merge(collect,t(collect_mz),
                             by.x=c('collect'),by.y=('collect_mz'),all=TRUE)
  }else{ # No mature cells present
    collect_mz<-collect_cz
    summary_mz<-rep(0,length(collect_cz))
    collect_mz<-data.frame(rbind(collect_mz,summary_mz))

    collect<-merge(collect,t(collect_mz),
                   by.x=c('collect'),by.y=('collect_mz'),all=TRUE)
    warning('no mature cells seem to be present in the model output, adjust format will output MZ=0 on every sammple day')

  }

  collect[is.na(collect)]<-0


  # Site name
  Site<-rep(as.factor(Site),length(summary_cz))

  # Year  # currently only one year
  Year<-rep(unique(cells_modelled$Year),length(summary_cz))

  # define Species as "Model"
  Species_model<-rep(as.factor("Model"),length(summary_cz))

  # define Tree number as 100, hoping that this is a number that tree numbers for observations never reach.
  Tree_model<-rep(as.factor("100"),length(summary_cz))

  # construct sample number
  #Sample<-rep(c(1,2,3),length(summary_cz)/3) # triplicates
  Sample<-1:length(summary_cz)
  #Sample<-seq(1,length(unique(cells_observed$DY))-1,1) # hack, somehow model does not output the last sample date..
  #Sample<-as.data.frame(Sample)
  #Sample<-as.integer(Sample[rep(1:nrow(Sample),each=3),])

  # construct days of the year
  DY<-unique(cells_modelled$day)
  #DY[length(DY)+1]<-360
  # DY<-head(DY,-1)
  # DY<-as.data.frame(DY)
  # DY<-DY[rep(1:nrow(DY),each=3),] # triplicates

  # construct repetition factor
  #RF<-as.factor(rep(c(1,2,3),length(summary_cz)/3)) # triplicates
  RF<-rep(as.factor(1),length(summary_cz))

  # construct quality measure
  # assume a quality value of 0.5 for all modelled values.
  PR<- rep(0.5,length(summary_cz))


  cells_modelled<-data.frame(Site=Site,
                             Year=Year,
                             Species=Species_model,
                             Tree=Tree_model,
                             Sample=Sample,
                             DY=DY,
                             RF=RF,
                             CZ=collect$summary_cz,
                             EZ=collect$summary_ez,
                             WZ=collect$summary_wz,
                             MZ=collect$summary_mz,
                             PR= PR)


  return(cells_modelled)

}
```

#Plot  Fig 2

```{r Fig2, fig.cap="Example year of the model input dynamics and how the outputs ( cell numbers, volume and mass increase follow these dynamics and generate density." }


# Graph layout inspired by Wilkinson et al 2015
# load model input and select site Grandfontaine

load('data/DH_model_ins.lst.RData')

# crude run of DH-model

DH_ins_weekly<-DH_model_ins.lst$Inputs_GRA_3years
y=3
params<-DH_model_ins.lst$Parameters$best
params_DH<-DH_model_ins.lst$Parameters# for table 2 below

Tair<-DH_ins_weekly$Tair
Rw<-DH_ins_weekly$SW
Cpool<-DH_ins_weekly$Cpool

n=53
D_n<-rep(0,(n*y) )
D_v<-rep(0,(n*y) )
D_m<-rep(0,(n*y) )


# hand over parameters
Tmin = params[1] #  # °C Temperature below with cambial activity, volume and mass increment do not occur.
Rwmin = params[2] # ( -) minimum relative soil moisture at which cambial activity, volume and mass increment do not occur.
D_n_max = params[3]
b = params[4]
D_v_max = params[5]
D_m_max = params[9]
delta = params[6]
chi = params[7]
R_w_crit = params[8]


#get relative soil moisture values as done in Wilkinson et al 2015
Rw<-1-1/(1+(Rw/R_w_crit)^chi)


ds<-c(1:(y*n))

# run DH-model

for(i in 1:(n*y)){

  if(Tair[i] >= Tmin & Rw[i] >= Rwmin) {

    D_n[i]<- D_n_max * (1-(exp( -b *(Tair[i]-Tmin) )))

    D_v[i]<-D_v_max * (Rw[i])

    D_m[i]<-D_m_max * (1- exp(-delta*Cpool[i]))

  }
}


# prepare output and plotting

Tair.df<-data.frame(Tair=Tair,dates=ds,D_n=D_n)
Rw.df<-data.frame(Rw=Rw,dates=ds,D_v=D_v)
Cpool.df<-data.frame(Cpool=Cpool,dates=ds,D_m=D_m)

Incr<-D_n*D_v
Dens<-(D_m/D_v)*1000 # to convert dm^3 (Wilkinso 2015) # m^3 ( Cuny et al 2014)
Dens.df<-data.frame(Dens=Dens,dates=ds)



# select last year only for plotting

Tair.df<-Tair.df[(2*53+1):(3*53),]
Rw.df<-Rw.df[(2*53+1):(3*53),]
Cpool.df<-Cpool.df[(2*53+1):(3*53),]
ds<-seq(as.Date("2009-01-01"),as.Date("2010-01-01"),7)
Incr<-Incr[(2*53+1):(3*53)]
Dens<-Dens[(2*53+1):(3*53)] # to convert dm^3 (Wilkinso 2015) # m^3 ( Cuny et al 2014)
Dens.df<-data.frame(Dens=Dens,dates=ds)


  par(mfrow=c(4,1),mar=c(0,5,0,5),oma=c(4,0,1,0))

  plot(Tair.df$dates,Tair.df$Tair,ylim=c(0,30),type="l",xaxt='n',xlab="",xaxs="i",yaxs="i",ylab="")
  mtext("Temperature (°C)",side=2,col="black",cex=1.2,line=3,outer=FALSE)
  abline(h=25,col = "lightgray", lty = 3)
  abline(h=2.5,col = "lightgray", lty = 3)
  par(new = T)
  plot(Tair.df$D_n,col="red",ylim=c(0.0,1.5), type ="p",xaxt='n',xlab="",yaxt='n',ylab="",xaxs="i",yaxs="i")
  mtext("cells/week",side=4,col="red",cex=1.2,line=3.4,outer=FALSE)
  axis(4,ylim=c(0.0,1.5),col="red",col.axis="red",las=1)


  plot(Rw.df$dates,Rw.df$Rw,ylim=c(0,1.52), type="l",xaxt='n',xlab="",xaxs="i",yaxs="i",ylab="")
  mtext("Rw (-)",side=2,col="black",cex=1.2,line=3,outer=FALSE)
  abline(h=0.5,col = "lightgray", lty = 3)
  par(new = T)
  plot(Rw.df$date,Rw.df$D_v,col="red",ylim=c(0.0,0.0074),xaxt='n',xlab="",yaxt='n',ylab="",xaxs="i",yaxs="i")
  mtext(expression(paste(Delta, " volume" )),side=4,col="red",cex=1.2,line=4,outer=FALSE)
  mtext("(m3/week)",side=4,col="red",cex=1.2,line=5.4,outer=FALSE)
  axis(4, ylim=c(0.0,0.0074), col="red",col.axis="red",las=1)


  plot(Cpool.df$dates,Cpool.df$Cpool,ylim=c(0,4),type="l",xaxt='n',xlab="",xaxs="i",yaxs="i",ylab="")
  mtext("Cpool (Kg[C])",side=2,col="black",cex=1.2,line=3,outer=FALSE)
  #lines(Ci, col="grey",lty=3)
  par(new = T)
  plot(Cpool.df$D_m,col="red",ylim=c(0.0,0.0052),xaxt='n',xlab="",yaxt='n',ylab="",xaxs="i",yaxs="i")
  mtext(expression(paste(Delta,"mass")), side=4 ,col="red",cex=1.2,line=4,outer=FALSE)
  mtext("(kg/week)",side=4,col="red",cex=1.2,line=5.4,outer=FALSE)
  axis(4, ylim=c(0.0,0.0052), col="red",col.axis="red",las=1)

  par(mar=c(3,5,0,5))
  plot(Dens.df$dates,Dens.df$Dens,ylim=c(0.0,1200),col="red",ylab="",yaxt='n',xaxs="i",yaxs="i")
  mtext("Density (kg/m3)",side=4,col="red",cex=1.2,line=4,outer=FALSE)
  axis(4, ylim=c(0.0,1200), col="red",col.axis="red",las=1)
  mtext(side=1,"2009",line= 2.3)

```


#Fig 3

```{r Fig3 ,fig.cap="Modelled and observed density profiles within tree rings for years 2007 to 2009."}

  #Plot Fig X:


  load(file='data/GRA_PISY_DENS.lst.RData')


  # when other density measures are saved in the above format, this plot can easily visualise them.
  index<-c(2007,2008,2009)
  par(mfrow=c(4,1),mar=c(0,4.5,0,40),omar=c(0,2.7,4,0))
  for ( i in 1:3){

    subs<-GRA_PISY_DENS.lst[[i]]
    Obs_mean<-subs[("Obs_mean"),]
    Obs_sd<-subs[("Obs_sd"),]
    Model<-subs[("Model"),]
    plot(Model, type ="l",ylim=c(0,1300),xaxt='n',xlab="", col="red",ylab="",xaxs="i",yaxs="i")
    xx<-c(1:20,20:1)
    # prepare for plotting sd error around mean + plot
    sd_above<-Obs_mean+Obs_sd
    sd_below<-Obs_mean-Obs_sd
    yy<-c(rep(0,length(sd_above)),rev(sd_above))
    polygon(xx, yy, col='lightgrey',border=NA)
    yy<-c(rep(0,length(sd_below)),rev(sd_below))
    polygon(xx, yy, col='white',border=NA)

    # replot model on top
    lines(Model, type ="l",col="red",xaxs="i",lwd=2.4,yaxs="i")
    # plot mean
    lines(Obs_mean, col= "black",xaxt='n',lwd=2.4,xlab="",xaxs="i",yaxs="i")
    mtext(side=3,line=-1.5,index[i],adj=0,cex=1.2)

  }
  axis(1, at=seq(0,20,5), labels=c(0.0, 0.25, 0.5, 0.75, 1))

  mtext("rel. position in tree ring",side=1,line=3,cex=1.8)
  plot(1, type="n", axes=F, xlab="", ylab="")
  mtext ("Density (Kg/m3)", side=2, cex=1.8, line=2.4,adj =0, at=2.2)
  legend("center",legend= c("DH-model", "Observed mean density"), cex=1,col =c("red","black") ,fill=c("red","black"),horiz=TRUE)


```





#Fig 4

```{r Fig4, fig.cap="Modelled and observed maximum density values for years 2007 to 2009.",eval=FALSE}

  load(file='data/GRA_PISY_TRW_MXD_NR.lst.RData')

  MXD_table     <- GRA_PSY_TRW_MXD_NR.lst$MXD_table

  par(mfrow=c(4,1),mar=c(0,4.5,0,10),oma=c(0,2.7,4,0))

  maxD<-max(MXD_table$Model+MXD_table$obs_stdev,MXD_table$obs+MXD_table$obs_stdev)+100
  minD<-min(MXD_table$Model-MXD_table$obs_stdev-100)
  plot(MXD_table$years,MXD_table$Model, col="red",lwd=2.3,type="o", ylab="",ylim=c(minD,maxD))
  lines(MXD_table$years,MXD_table$obs, col="black",lwd=2.3, type ="o",xaxt='n',xlab="", ylab="")
  segments(MXD_table$years,MXD_table$obs-MXD_table$obs_stdev,MXD_table$years,MXD_table$obs+MXD_table$obs_stdev)
  mtext(side=2, "Maximum density \n (kg/m3)",cex=1.2,line=3)
  mtext(side=1, "Years",line=3,cex=1.4)
  mtext(side=3,line=-2.2,adj=0)


```




#Fig 5

```{r Fig5 ,fig.cap=" VS model: Cambial blocks’ framework for  position-dependent evaluation of G into absolute growth rate"}

  # imagine 20 cells
  j<- seq(0:20)
  # code up the cambial zone image

  #exponential function of Vmin ( Camb50.for, Vaganov et al 2011)
  b5=1
  b8=0.55
  b9=0.045#0.035
  #linear function (Camb50, parametersin CMB50)
  b7=0.35 # corresponds to table 7.2 b1, value used there : 0.42
  b6=0.12 # corresponds to table 7.2 b2, value used there : 0.25

  V_cr =0.04

  zone_Vmin_Camb50<-b9*exp(b8*j*b5)
  zone_V0_Camb50<-b7+ b6*j


  par(mfrow=c(1,2),mar=c(8,4,8,0.5),oma=c(3,3,2,0))

  plot(zone_Vmin_Camb50,type="l",ylim=c(0,3),xlim=c(1,20),col="orange",lwd=3.2,xaxs="i",yaxs="i",xlab="",ylab="")
  lines(zone_V0_Camb50,lwd=3.2)
  abline(h=V_cr,col="red",lwd=3.2)
  #mtext(side=3,line=0.5,"Position dependent absolute growth rate",outer=TRUE,cex=1.3)
  mtext(side=2,line=3, "Absolute growth rate \n(µm/day)",cex=2)
  mtext( "cell position", side=1 ,line=3.2,cex=2)
  mtext(side=3,line=-1,"B",adj=0,cex=1.2)
  plot(1, type="n", axes=F, xlab="", ylab="")
  legend("left",legend=c("V_min","V_0","V_cr"),col=c("orange","black","red"),fill=c("orange","black","red"))



```
 
 
#Fig 6:

```{r fig6, fig.cap="relative growth rates (t,w,e) , integrated growth rate G and cell numbers (N) throughout year 2009 at WAL(black), ABR (green) & GRA(blue)"}
 # Graph layout inspired by Evans et al 2006

  load(file='data/VS_model_output.RData')

  # retrieve Model output
  loc_Walscheid_360m     <- VS_model_output$loc_Walscheid_360m
  loc_Abreschviller_430m <- VS_model_output$loc_Abreschviller_430m
  loc_Grandfontaine_650m <- VS_model_output$loc_Grandfontaine_650m


  # cambial_growth_rate used to hold  g_rate_t
  # enlargement_rate used to hold g_rate_w
  # thickening_rate used to hold g_rate_e

  # only plot year 2009: [365*2+1:365*3]
  nyears=1
  start_date<-"2009-01-01"


  par(mfrow=c(5,1),mar=c(0,5,0,5),oma=c(4,0.5,1,0))
  sites<-c('loc_Walscheid_360m','loc_Abreschviller_430m','loc_Grandfontaine_650m')

  g_rate_t_W <- get(sites[1])$growth_rates$cambial_growth_rate[(365+366+1):(365*2+366)]
  g_rate_t_A <- get(sites[2])$growth_rates$cambial_growth_rate[(365+366+1):(365*2+366)]
  g_rate_t_G <- get(sites[3])$growth_rates$cambial_growth_rate[(365+366+1):(365*2+366)]

  plot(g_rate_t_W,type="l",xlab="",xaxt="n",ylim=c(0,1.1),lty=1, ylab="g_rate_t",cex.lab=1.5)
  lines(g_rate_t_A, col="green",lty=2)
  lines(g_rate_t_G, col="blue",lty=3)

  g_rate_w_W <- get(sites[1])$growth_rates$enlargement_rate[(365+366+1):(365*2+366)]
  g_rate_w_A <- get(sites[2])$growth_rates$enlargement_rate[(365+366+1):(365*2+366)]
  g_rate_w_G <- get(sites[3])$growth_rates$enlargement_rate[(365+366+1):(365*2+366)]

  plot(g_rate_w_W,type="l",xlab="",xaxt="n",ylim=c(0,1.1),lty=1, ylab="g_rate_w",cex.lab=1.5)
  lines(g_rate_w_A, col="green",lty=2)
  lines(g_rate_w_G, col="blue",lty=3)

  g_rate_e_W <- get(sites[1])$growth_rates$thickening_rate[(365+366+1):(365*2+366)]
  g_rate_e_A <- get(sites[2])$growth_rates$thickening_rate[(365+366+1):(365*2+366)]
  g_rate_e_G <- get(sites[3])$growth_rates$thickening_rate[(365+366+1):(365*2+366)]

  plot(g_rate_e_W,type="l",xlab="",xaxt="n",ylim=c(0,1.1),lty=1, ylab="g_rate_e",cex.lab=1.5)
  lines(g_rate_e_A, col="green",lty=2)
  lines(g_rate_e_G, col="blue",lty=3)

  #to obtain Grate for all 3 sites
  sites_L<-c('W','A','Wcells','Acells')

  # prepare the large data frame (W and A have on emore year of met data)
  nyears<-round(length(g_rate_t_W)/365, digits=0)
  Gplot<-data.frame(matrix(0,ncol=5,nrow=length(g_rate_t_W[(365+366):(365*2+366)])))
  colnames(Gplot)<-c('Time',sites_L)
  G<-rep(0,365*nyears)

  # set timestamp to enable better plotting
  #start_date<-"2007-01-01"
  Gplot$Time<-create_Timestamp(start_date,nyears)
  Gplot$W <- get(sites[1])$growth_rates$G_env[(365+366):(365*2+366)]
  Gplot$A <- get(sites[2])$growth_rates$G_env[(365+366):(365*2+366)]
  Gplot$Wcells<-get(sites[1])$growth_rates$`cumulative Cell#`[(365+366):(365*2+366)]
  Gplot$Acells<-get(sites[2])$growth_rates$`cumulative Cell#`[(365+366):(365*2+366)]

  # add the shorter data frame
  Gshort<-data.frame(matrix(0,ncol=2,nrow=length(get(sites[3])$growth_rates$G_env[(365+366):(365*2+366)])))
  names(Gshort)<-c("G","Gcells")
  Gshort$Time<- create_Timestamp(start_date,nyears)
  Gshort$G<-get(sites[3])$growth_rates$G_env[(365+366):(365*2+366)]
  Gshort$Gcells<-get(sites[3])$growth_rates$`cumulative Cell#`[(365+366):(365*2+366)]
  Gplot<-merge(Gplot, Gshort, by.x = "Time", all=TRUE )

  # remove cells carried over from last year
  Gplot$Wcells[1]<-0
  Gplot$Acells[1]<-0
  Gplot$Gcells[1]<-0

  # plot
  plot(Gplot$Time, Gplot$W, type = "l", ylab = "G", ylim=c(0,1.1), lty=1, xlab="", xaxt="n",cex.lab=1.3)
  lines(Gplot$Time, Gplot$A, col="green", type = "l", ylab = "G", ylim=c(0,1.1), lty=2)
  lines(Gplot$Time, Gplot$G, col="blue", type = "l", ylab = "G", ylim=c(0,1.1), lty=3)

  plot(Gplot$Time, Gplot$Wcells, type = "l",ylab="N",cex.lab=1.5)
  lines(Gplot$Time, Gplot$Acells, col = "green")
  lines(Gplot$Time, Gplot$Gcells, col = "blue")
  mtext("2009",cex=1.2,line=-14.5)

```


#Fig 7:

```{r fig7, fig.cap="Wood formation phenology observations for Pinus sylvestris at Grandfontaine in 2009 (left) and (where cell type available) the corresponding VS-model output (right) plotted using CaviaR."}



  load(file='data/GRA2009_Cell_Count.RData')

  # now, adjust the format to make it comparable for CaviaR.
  cells_modelled<-adjustFormat(loc_Grandfontaine_650m$microcore_collection,2009,'GRA')
  # hack: move what is in EZ to MZ to better visualise that no EZ or WZ are modelled by the VS-model.
  names(cells_modelled)<-c("Site", "Year", "Species", "Tree", "Sample","DY", "RF", "CZ", "MZ",  "WZ", "EZ", "PR" )

  # remove sampling day 365, stretches the plot too much:
  cells_modelled<-cells_modelled[cells_modelled$DY!=365,]


  plotWoodFormationDynamics(GRA2009_Cell_Count,level="MvM")

  plotWoodFormationDynamics(cells_modelled)

```




#Fig 8:

```{r fig8 ,fig.cap="Modelled and observed number of cells and ring width for years 2007 to 2009."}


  load(file='data/GRA_PISY_TRW_MXD_NR.lst.RData')
  #unlist(GRA_PSY_TRW_MXD_NR.lst[[1]]) doesn't work?!

#mean cell size across all years for PISY at GRA
D_MEAN= 26.28087

  TRW_table     <- GRA_PSY_TRW_MXD_NR.lst$TRW_table
  MXD_table     <- GRA_PSY_TRW_MXD_NR.lst$MXD_table
  cell_nr_table <- GRA_PSY_TRW_MXD_NR.lst$cell_nr_table

  cell_nr_table$VS_model <- as.numeric(loc_Grandfontaine_650m$cell_numbers)
  TRW_table$VS_model <- as.numeric(D_MEAN*loc_Grandfontaine_650m$cell_numbers/1000) # change units from µm to mm

  # plot
  par(mfrow=c(4,1),mar=c(0,4.5,0,40),oma=c(0,2.7,4,0))

  maxN<-max(cell_nr_table$tot_cells_model,cell_nr_table$Mean)+max(cell_nr_table$Sd)+5
  minN<-min(cell_nr_table$tot_cells_model,cell_nr_table$Mean)-max(cell_nr_table$Sd)-5

  plot(cell_nr_table$years,cell_nr_table$tot_cells, lwd=2.3,col="red",type="o",xaxt='n',xlab="", ylab="",ylim=c(minN,maxN))
  lines(cell_nr_table$years,cell_nr_table$Mean, lwd=2.3,col="black", type ="o",xaxt='n',xlab="")
  segments(cell_nr_table$years,cell_nr_table$Mean-cell_nr_table$Sd,cell_nr_table$years,cell_nr_table$Mean+cell_nr_table$Sd)
  lines(cell_nr_table$years,cell_nr_table$VS_model, lwd=2.3,col="grey", type ="b",xaxt='n',xlab="")
  mtext(side=2, "Number of cells",cex=1.2,line=3)
  mtext(side=3,"A",line=-2.2,adj=0)

  maxRW<-max(TRW_table$TRW_model,TRW_table$TRW_obs)+max(TRW_table$TRW_obs_stdev)+0.2
  minRW<-min(TRW_table$TRW_model,TRW_table$TRW_obs)-max(TRW_table$TRW_obs_stdev)-0.2
  plot(TRW_table$years,TRW_table$TRW_model,type="o",lwd=2.3,cex.lab=5, ylab="",col="red",ylim=c(minRW,maxRW),xlab="")
  lines(TRW_table$years,TRW_table$TRW_obs,lwd=2.3,type="o",col="black")
  segments(TRW_table$years,TRW_table$TRW_obs-TRW_table$TRW_obs_stdev,TRW_table$years,TRW_table$TRW_obs+TRW_table$TRW_obs_stdev)
  lines(TRW_table$years,TRW_table$VS_model, lwd=2.3,col="grey", type ="b",xaxt='n',xlab="")
  mtext(side=2, "Ring width (mm)",cex=1.2,line=3)
  mtext(side=3,"B",line=-2.2,adj=0)
  mtext(side=1, "Years",line=3,cex=1.4)
  plot(1, type="n", axes=F, xlab="", ylab="")
  legend("center", legend=c("DH-model","VS-model","observations"), cex=1,col=c("red","grey","black"),fill=c("red","grey","black"),horiz=TRUE)



```




  # Table 2

  Symbol  | Unit | Description | Value
  --------|------|-------------|-------
    $T_{air}$         | °C         | Weekly mean air temperature | input
  $\Delta_{n,i}$    | cells      | Number of cells produced per week (i) | output
  $Tmin$            | °C         | Minimum air temperature | `r params_DH[1,1]`
  $\Delta_{n,max}$  | cells/week | Maximum number of cells produced per week | `r params_DH[3,1]`
  $\beta$           | /°C        | Sensitivity of cell division to temperature | `r params_DH[4,1]`
  $R_{w,i}$        | vsoil/ vmax soil | Relative water availability | input
  $\Delta_v$        | $m^3$      | Tree volume gain within a week | output
  $\Delta_{v,max}$  | $m^3/week$ | Maximum tree volume gain per week  | `r params_DH[5,1]`
  $Cpool_{i}$       | kg[C]      | NSC pool size per week | input
  $\Delta_{m,i}$    | kgDW       | Tree mass increment within a week | output
  $\Delta_{m,max}$  | kgDW/week  | Maximum tree mass increment per week | `r params_DH[9,1]`
  $\delta$          | /kgDW      | Sensitivity of cell wall thickening to Carbon pool | `r params_DH[6,1]`
  $Dens_i$          | kg/m^{3}   | Density produced during week _i_ | output
  $Incr$            | mm         | Ring width increment during week _i_ | output
  $g\_rate\_e$      | (-)        | relative growth rate modifier based on daylength | variable
  $g\_rate\_t$      | (-)        | relative growth-rate modifier based on temperature | variable
  $g\_rate\_w$      | (-)        | relative growth-rate modifier based on soil moisture | variable
  $G$               | (-)        | relatige integrated growth rate | variable
  $D_{mean}$        | µm         | Observed mean cell diameter across study years | 26.28087
  $N$               | cells      | Number of cells | output
  $TRW$             | mm         | Treering width  | output
b9| - | exponential function of Vmin (  Vaganov et al 2011) | `r b9 `
b8| - | exponential function of Vmin (  Vaganov et al 2011) | `r b8 `
b5| - | exponential function of Vmin (  Vaganov et al 2011) | `r b5 `
b7| - | linear function (Camb50, parametersin CMB50) | `r b7 `
b6| - | linear function (Camb50, parametersin CMB50) | `r b6 `

